\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-05 paper/draft.tex
Add figure

>>>>

\begin{figure*}[t]
  \centering
   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
  \caption{
    \textbf{Analysis overheads.}
    The plot compares a series of modules from single-library programs taken from Jalangi between three setups:
		(i) Vanilla JavaScript, (ii) global-use analysis using Jalangi, (iii) global-use analysis using \sys.
    Global-use analysis is a relatively simple analysis that tracks accesses of global variables in the program~\cf{meso}.
  }
  \label{fig:meso}
  \vspace{-3mm}
\end{figure*}
